Interval Probability for Fuzzy Quantum Theories

### 2016-07-30 prob.tex
prob.tex Update the definiton of convex...

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the
  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
  consider variants constructed over finite
  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probability measures~\cite{PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1983,Mermin2007} and the map is given by:
  $P \mapsto \ip{\psi}{P\psi}$.
\item given a probability measure $\mu$
  mapping each event $P$
  to a probability, is there a \emph{unique} state $\psi$
  such that $\mu(P)
  =
  \ip{\psi}{P\psi}$? In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
Every convex interval-valued probability measure has a nonempty core,
where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
and $l\left(E_{1}\cup E_{2}\right)\ge l\left(E_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{2}\right)\tensor*[_{\mathbb{R}}]{-}{}l\left(E_{1}\cap E_{2}\right)$
for all $E_{1},E_{2}\in\events$.\qed\end{thm}

@@

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
Given a Hilbert space $\Hilb$ with the set of quantum events~$\events$,
and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
probability measure} is a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that: 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$, 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$, 
\item for any projection $P$, 
\begin{equation}
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Complement}
\end{equation}
\item for a set of mutually orthogonal projections $P_{i}$, we have 
\begin{equation}
\bar{\mu}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\footnote{Let $\bar{\mu}\left(P\right)=\left[l\left(P\right),r\left(P\right)\right]$.
Then, $\bar{\mu}$ is called convex if $l\left(P_{1}P_{2}\right)\ge l\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(P_{2}\right)\tensor*[_{\mathbb{R}}]{-}{}l\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)$
for all commuting $P_{1},P_{2}\in\events$. We may further define
a quantum Dempster-Shafer probability measure, and a quantum Dempster-Shafer
probability measure is always convex.}
\end{itemize}
As before, we will only define a quantum interval-valued probability
measure with preposing $\mathscr{I}$ when we want to compare a quantum
probability measure and a quantum interval-valued probability measure.
\qed\end{definition}

>>>>

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the uncountable
and uncomputable complex numbers $\mathbb{C}$), we will consider
variants constructed over finite fields~\cite{DQT2014,geometry2013}. 
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probability measures~\cite{PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1983,Mermin2007} and the map is given by:
  $P \mapsto \ip{\psi}{P\psi}$.
\item given a probability measure $\mu$
  mapping each event $P$
  to a probability, is there a \emph{unique} state $\psi$
  such that $\mu(P)
  =
  \ip{\psi}{P\psi}$? In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
Every convex interval-valued probability measure has a nonempty core,
where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is convex if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\ge\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$.\qed\end{thm}

@@

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
Given a Hilbert space $\Hilb$ with the set of quantum events~$\events$,
and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
probability measure} is a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that: 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$, 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$, 
\item for any projection $P$, 
\begin{equation}
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Complement}
\end{equation}
\item for a set of mutually orthogonal projections $P_{i}$, we have 
\begin{equation}
\bar{\mu}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\footnote{$\bar{\mu}$ is called convex if $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\ge\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
for all commuting $P_{1},P_{2}\in\events$. We may further define
a quantum Dempster-Shafer probability measure, and a quantum Dempster-Shafer
probability measure is always convex.}
\end{itemize}
As before, we will only define a quantum interval-valued probability
measure with preposing $\mathscr{I}$ when we want to compare a quantum
probability measure and a quantum interval-valued probability measure.
\qed\end{definition}
